Characterization of foreign direct investment in Mozambique and implications

### 2015-10-16 paper.Rmd
little things

@@

@@

@@

par(mfrow = c(1,3))
par(mar = c(4,0,4,0))
plot(temp, col = colorfy(temp$y2000), border = NA); title(main = '2000')
plot(temp, col = colorfy(temp$y2005), border = NA); title(main = '2005')
plot(temp, col = colorfy(temp$y2009), border = NA); title(main = '2009')
par(mar = c(5,4,2,2))

legend_vec <- seq(6000, 24000, 6000)
legend('right',
       fill = cols[legend_vec],
       bty = 'n',
       border = NA,
       legend = legend_vec)
```

>>>>

Most of recent growth has come in the "extractive" industries, a term encompassing...  XXX

@@

The principal foreign firms operating in this space are YYY YYY YYY.

@@

Growth has been similarly large in all districts.  From 2000 to 2009, GDP approximately doubled, with the greatest growth occurring in Inhambane (119% growth from 2000 to 2009), and the least robust grwoth in Nampula (95%).

@@

par(mfrow = c(1,3))
par(mar = c(4,0,2,1))
plot(temp, col = colorfy(temp$y2000), border = NA); title(main = '2000')
plot(temp, col = colorfy(temp$y2005), border = NA); title(main = '2005')
plot(temp, col = colorfy(temp$y2009), border = NA); title(main = '2009')
par(mar = c(5,4,2,2))

legend_vec <- seq(8000, 24000, 8000)
legend('right',
       fill = cols[legend_vec],
       bty = 'n',
       border = NA,
       legend = paste0(legend_vec/1000,'K'),
       ncol = 1,
       title = 'GDP')
```
